---
title: "How to plot points in a map from _ozmaps_"
author: "JR Ferrer-Paris (https://github.com/jrfep)"
date: 2021-06-21
output:
  pdf_document: default
  html_document: default
---

Package `ozmaps` can be used to load simple mapdata for Australia.

Check package documentation at: https://www.rdocumentation.org/packages/ozmaps/versions/0.4.0

## Required packages

```{r}
# install.packages(c("ozmaps"))
require(ozmaps)
require(ggplot2)
require(dplyr)

```

## Reproducible data

Extract map data for a single state from the `ozmap_states` data:

```{r}
ozmap_states %>% filter(NAME=='Queensland') -> Queensland_map
```

Create a tibble with the point data (coordinates must be in the same geographic projection as the map)

```{r}
locations <- tibble(lon=c(144,145,147,140),
                    lat=c(-18,-22,-27,-23),
                    var1=c(700,100,1000,500),
                    var2=factor(c(1,1,2,3)))
```

## Solution

Very simple map with outline and data points:

```{r}
ggplot() +
  geom_sf(data = Queensland_map, show.legend = FALSE) +
  coord_sf() +
  geom_point(data=locations,aes(x=lon,y=lat,size=var1,color=var2))
```

Solution adapted from: https://ggplot2-book.org/maps.html

## Debugging info

Check the R session info:

```{r}
sessionInfo()
```
