---
title: "Working with a `ggstream` plot"
author: JR Ferrer-Paris (https://github.com/jrfep)
date: 2021-06-21
output:
  pdf_document: 
    fig_width: 4
    fig_height: 3
  html_document: default
editor_options: 
  chunk_output_type: console
---

We want to test the package `ggstream` and work with the function `geom_stream_labels`.

Check this post: https://r-charts.com/evolution/ggstream/

Package documentation: https://rdrr.io/github/davidsjoberg/ggstream/man/geom_stream.html

## Required packages

```{r}
# install.packages("remotes")
# remotes::install_github("davidsjoberg/ggstream")
library(ggstream)
# install.packages("ggplot2")
library(ggplot2)
```

## Reproducible data

Run example with a default dataset:
```{r}
ggplot(blockbusters, aes(x = year, y = box_office, fill = genre)) +
  geom_stream()
```


## Solution

We can save the plot to an object and then add/change elements, for example:

### Add labels

```{r}
my.plot <- ggplot(blockbusters, aes(x = year, y = box_office, fill = genre)) +
  geom_stream()

my.plot + geom_stream_label(aes(label = genre))
```

### Change type of stream plot

This will not work with a different type of plot

```{r}
my.plot <- ggplot(blockbusters, aes(x = year, y = box_office, fill = genre))
my.plot + geom_stream(type='ridge') + geom_stream_label(aes(label = genre))
```

unless...

```{r}
my.plot + geom_stream(type='ridge') + geom_stream_label(aes(label = genre),type='ridge')
```

Check another type

```{r}
my.plot + geom_stream(type='proportional') + geom_stream_label(aes(label = genre),type='proportional')
```


### Change colors and add border

```{r}
cols <- c("#FFB400", "#FFC740", "#C20008", "#FF020D", "#13AFEF")
my.plot <- my.plot + geom_stream(type='ridge',color=1,lwd=0.25) + geom_stream_label(aes(label = genre),type='ridge')
my.plot + scale_fill_manual(values = cols)
```

### Change theme

Adapt the colors for a different theme:
```{r}
## you could use RColorBrewer::brewer.pal(5,"Pastel")
cols <- c("#FBB4AE", "#B3CDE3", "#CCEBC5", "#DECBE4", "#FED9A6")
my.plot + scale_fill_manual(values = cols) + theme_dark()
```



## Debugging info

Check the R session info:

```{r}
sessionInfo()
```
